%-------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%-------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[letter,10pt]{article}

%-------------------------------------------------------------------------------
%	FONT
%-------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%-------------------------------------------------------------------------------
%	PACKAGES
%-------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.95]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

\newenvironment{mylist}[1][]
    {\itemize[nosep, wide=0pt, leftmargin=*, after=\strut]}
    {\enditemize}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colors for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
% \usepackage{showframe}

%-------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%-------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%-------------------------------------------------------------------------------
%	TITLE
%-------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\huge{Liam Strand} \\[5pt]
\href{https://github.com/liam-strand}{\raisebox{-0.05\height}\faGithub\ liam-strand} \ $|$ \ 
\href{https://liam-strand.github.io}{\raisebox{-0.05\height}\faGlobe \ liam-strand.github.io} \ $|$ \ 
\href{mailto:strandliam@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ strandliam@gmail.com} \ $|$ \ 
\href{tel:+14084381125}{\raisebox{-0.05\height}\faMobile \ +1 (408) 438-1125} \\
\end{tabularx}

%-------------------------------------------------------------------------------
% INTERESTS / KEYWORDS / SUMMARY
%-------------------------------------------------------------------------------

% \section{Interests}
% This CV is automatically generated and deployed using the \href{https://github.com/jitinnair1/autoCV}{autoCV} template along with GitHub Actions such that a new version of the CV is compiled, published and ready for use when the cv.tex file is updated. For details, \href{https://github.com/jitinnair1/autoCV}{click here}.

\section{Education}
\begin{minipage}[t]{\linewidth}
    \textbf{BS in Computer Science, Tufts University School of Engineering (ABET) GPA: 3.97/4.00} \hfill \normalsize 2020 - 2024 \\
    \small Data Structures/Algorithms, Machine Structure and Assembly Language Programming, Software Engineering, Concurrent Programming, Parallel Computing, Computational Theory, Programming Languages, Cybersecurity, Machine Learning, Spatial Audio Software. \qquad \qquad \qquad \qquad Spring 2024: Operating Systems, Quantum Computing, Network Security, Computer Engineering. (\textbf{Dean's List 7/7 semesters})
% Summer/Fall 2020 & Swift 2, iOS development bootcamp, Udemy London App Brewery
% Summer 2019 & Python Scripting, Rice University/Coursera	
\end{minipage}

%-------------------------------------------------------------------------------
% EXPERIENCE
%-------------------------------------------------------------------------------

\section{Work Experience}
\begin{minipage}[t]{\linewidth}
    \textbf{AeroVironment, Inc. \textbar \ Software Engineering Intern \textbar \ Wilmington, MA} \hfill Summer 2023 
    \begin{mylist}
        \item Demonstrated that costs of aerial robotics product can be dramatically reduced by transitioning to COTS hardware. 
        \item Led hardware bringup and software integration effort. Created development pipelines and containers using Docker and GitLab. 
        \item Led porting of large, high-performance C++ applications to new distributed hardware environment. 
        \item Refactored communication protocol to improve design and resiliency, and resolved complex Linux kernel driver incompatibilities.
    \end{mylist}
\end{minipage}


\begin{minipage}[t]{\linewidth}
    \textbf{Bioinformatics \& Computational Biology Group, Tufts University \textbar \ Summer Scholar \textbar \ Medford, MA} \hfill Summer 2022
    \begin{mylist}
        \item Led multi-institutional team. Delivered syntax validation, color highlighting, and auto-completion features.
        \item Implemented client/server architecture in Python, with a well-documented API to support new language features and editors. 
        \item Utilized beta tester feedback and automated regression testing frameworks.
        \item Presented \href{https://www.eecs.tufts.edu/~lstran01/files/context-sensitive.pdf}{manuscript} at MTSR 2023. Honorable Mention for CRA Outstanding Undergraduate Researcher. (\href{https://youtu.be/TFLdXxnaBlU}{Demo}) (\href{https://github.com/liam-strand/medford-language-server}{Repository})
    \end{mylist}
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{Computer Science Department, Tufts University \textbar \ Teaching Assistant \textbar \ Medford, MA} \hfill Fall 2021 - Present
    \begin{mylist} 
        \item Design and lead labs and review sessions for C and C++ machine structure and assembly language courses. 
        \item Teach debugging and performance analysis strategies using tools such as \texttt{gdb} and \texttt{valgrind}.
        \item Collaborate with faculty to develop course infrastructure, assessments, and assignments.
    \end{mylist}
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{Hither Creek Boatyard \textbar \ Data Collection/Analysis \textbar \ Madaket, MA} \hfill Summer/Winter 2018 - 2021
    \begin{mylist}
        \item Created and installed Point-Of-Sale system backup network allowing business to operate when primary internet service fails.
        \item Designed Yamaha outboard engine data collection methodology. Gathered, analyzed, and synthesized data for 18 engine models.
        \item Created accessible Yamaha outboard engine diagnostic charts. Recovered and transferred GPS chartplotter data. 
    \end{mylist}
\end{minipage}

%-------------------------------------------------------------------------------
% PROJECTS
%-------------------------------------------------------------------------------

\section{Projects}

\begin{minipage}[t]{\linewidth}
    \textbf{Rust Boggle Solver: \href{https://github.com/liam-strand/ruggle}{Ruggle}} \hfill 2023 \\
    Designed and built a highly optimized Boggle solver in Rust utilizing a serializable prefix tree (trie) data structure to encode a lexicon, a pruning graph-traversal algorithm, and a custom visualization system to display words as they appear on the board.
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{Assembly Emulator:} \href{https://github.com/liam-strand/comp-40-VM-Profiling}{\textbf{VM Profiling}} \hfill 2022 \\
    Built a simulated architecture emulator in C, and vastly improved performance using modern profiling techniques. (\href{https://youtu.be/OnzkSmFvxiM}{Demo})
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{Concurrent Simulations:} \href{https://github.com/liam-strand/cs121-p5\#metrosim2}{\textbf{MetroSim2}} and \href{https://github.com/liam-strand/cs-21-final-project}{\textbf{on-the-road-again}} \hfill 2022 \\
    Developed fully concurrent subway simulation in Java using communicating threads to represent trains, passengers, and stations. Designed and built traffic simulation using CSP in Erlang with Python visualization, communicating over serialized I/O. (\href{https://youtu.be/_JQW8edL14A}{Demo}) 
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \href{https://github.com/liam-strand/cs121-p3\#testing-in-java}{\textbf{Java Testing Framework}} \hfill 2022 \\
    Designed testing infrastructure: unit testing library, test generation framework, fluent assertion domain-specific language, test runner.
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{Python CLI Concurrent Queue Manager:} \href{https://github.com/liam-strand/HalliganHelper2}{\textbf{HalliganHelper2}} \hfill 2021 \\
    Developed CLI to manage FIFO queue of students requesting TA assistance in Python. Used shared files and file locks to prevent change conflicts. CLI automatically invokes relevant commands and imposes serialization. (\href{https://youtu.be/qPwZz3OVA7A}{Demo})
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{iOS Data Scraping App:} \href{https://github.com/liam-strand/IFR-Plate-Scrape}{\textbf{IFR Plate Scrape}} \hfill 2021 \\
    Built airport mapping app in Python using HTTP requests to retrieve FAA data, and BeautifulSoup to extract and present relevant information to user. Ported to iOS using Swift, leveraging built-in URL management and SwiftSoup. (\href{https://youtu.be/bDe3dsVyUok}{Demo})
\end{minipage}

\begin{minipage}[t]{\linewidth}
    \textbf{iOS Data Logging App:} \href{https://github.com/bstrand42/Log-Your-Catch}{\textbf{Log Your Catch}} \hfill 2020 \\
    Built iOS app to capture and record data to support fishery management using Apple Location Services and Google Firebase database services. Completed architecture design, UI design, system integration, authentication, and beta testing.
\end{minipage}

%-------------------------------------------------------------------------------
%	SKILLS
%-------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Languages:} & Assembly, C, C++, Erlang, Java, \LaTeX, Markdown, Python, Rust, StandardML, Swift, Unix/Shell Scripting \\
    \textbf{Tools/IDEs:} & Apple SDKs, Docker, \texttt{gdb}, \texttt{git}, GitHub, GitLab, GPU/CUDA, Jira, Linux/Unix, \texttt{valgrind}, VSCode, Xcode \\
    \textbf{Experienced In:} & Agile Development, Concurrent/Parallel Programming, Hardware Bringup, Profiling, Testing Methodologies
\end{tabularx}

%-------------------------------------------------------------------------------
%	COMMUNITY
%-------------------------------------------------------------------------------
\section{Community}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
    JumboCode & Leading team-driven application development for local non-profit organizations. \\[2.75pt]
    Faculty Interviewer & Asked to help assess candidates for tenure-track teaching faculty positions at Tufts University. \\[2.75pt]
    Engineering Ambassador & Selected to advise incoming and first-year engineering students. \\[2.75pt]
    Sustainable Nantucket & Migrated critical data from failing Windows 2007 server, verified data accuracy/accessibility. \\[2.75pt]
    Robotics & Led skills training: soldering, metal fabrication, carpentry, robot design, additive fabrication, and \qquad \qquad electronics. Mentored new team members. Coached new leaders. Created legacy training program. \\[2.75pt]
    Community Research & Collaborated on A1 vs A2 ruminant genetics study and planned/executed soil carbon testing at small sustainable dairy farm.
\end{tabularx}

%-------------------------------------------------------------------------------
%	PASSIONS
%-------------------------------------------------------------------------------
\section{Passions}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
    Theatre & Short Play Festival Reader/Judge: 2020 - Present \\[2.75pt]
    Choir & Concert and Chamber Choirs (Bass): 2016 - Present \\[2.75pt]
    Ensembles & Jazz/Rock Ensembles (Keyboard): 2015 - Present \\[2.75pt]
    Classical Piano & Certificate of Merit Awards (through Level 6) \\[2.75pt]
    Improvisation & MTAC Improvisation Festival (Piano) \\[2.75pt]
    Musical Direction \qquad \ \ \ & The Requiem Project (Founder and Director)
\end{tabularx}

%-------------------------------------------------------------------------------
%	REFERENCES
%-------------------------------------------------------------------------------
\section{References}
References available upon request.

%-------------------------------------------------------------------------------
%	PUBLICATIONS
%-------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}


% \vfill
% \center{\footnotesize Last updated: \today}

\end{document}
